\documentclass{tccv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{fontawesome}
\newcommand\SYMBOL[1]{\raisebox{-2pt}{\Large\ding{#1}}}

\begin{document}

\part{Manuel Arto}

% ABOUT ME
\section{About Me}

Master's student in Computer Science at the University of Bologna and part-time Full-stack Developer at Archeion.\newline
I have professional experience in software development, with specific interests in backend programming and blockchain. 

% WORK EXPERIENCE
\section{Work Experience}

\begin{eventlist}

     \item{Feb 2024 - Present}
     {\href{https://archeion.tech/}{Archeion}, Bologna}
     {Full-stack Web3 Developer} \\
     \textbullet~Built the entire MVP mobile app for vendors using Ionic and Angular in under 3 months. \\
     \textbullet~Improved creation of schemas for 10+ clients by designing a custom JSON schema form renderer. \\
     \textbullet~Designed a scalable URL shortening service, securing over 10 million active URLs. \\
     \textbullet~Migrated customer app to an SSR architecture and designed a Redis-backed cache for on-demand translation of labels. \\
     \textbullet~Spearheaded the ZONIA prototype for the EU-funded TrustChain project: developed a zero-trust multi-chain oracle system for IoT devices. \\
     \textbf{\textsc{NestJS · Redis · Solidity · Angular · WoT}}

     \item{Sep 2021 - Sep 2023}
     {\href{https://www.netservice.eu/}{Net Service}, Bologna}
     {Backend Developer} \\
     \textbullet~Managed a legal data platform used by over 40 credit institutions, maintaining 99.9\% uptime. \\
     \textbullet~Reduced infrastructure costs by 80\% by migrating from a monolith to a multitenant architecture. \\
     \textbullet~Developed and deployed a 5 microservices system using Spring Boot and OpenShift. \\
     \textbullet~Processed a data stream of more than 100 million records using MongoDB, PostgreSQL, ActiveMQ and ETL scripts. \\
     \textbullet~Achieved a 75\% code coverage using TDD via JUnit for new feature development. \\
     \textbf{\textsc{Spring Boot · OpenShift · MongoDB · PostgreSQL · ActiveMQ}}

\end{eventlist}


% SKILLS
\section{Skills}

\begin{factlist}

\item{Technical}
     {Python, Java, Solidity, Go, Node.js, Flutter, C++, Android, Docker, Linux, Design, Testing} \\

\item{Soft}
     {Teamwork, Communication, Adaptability, Time Management, Leadership}

\end{factlist}


% HOBBY
\section{Hobby}

Calisthenics, Chess, Manga, Movies and TV Series


% NEW PAGE
\newpage


% PERSONAL INFORMATION
\begin{keyvaluelist}{personal}
    \item[\faHome] Bologna, Italy
    \item[\faPhone] +39 3887833963
    \item[\faEnvelope] \href{mailto:manuelarto01@gmail.com}{manuelarto01@gmail.com}
    \item[\faGithub] \href{https://github.com/manuelarto}{GitHub}
    \item[\faLinkedin] \href{https://www.linkedin.com/in/manuel-arto-696012203/}{LinkedIn}
\end{keyvaluelist}


% EDUCATION
\section{Education}

\begin{yearlist}

\item[Master's Degree]{2023-2025}
     {Computer Science}
     {University of Bologna \newline GPA: 4.0}

\item[Bachelor's Degree]{2020-2023}
    {Computer Science}
    {University of Bologna}

\end{yearlist}


% SIDE PROJECTS
\section{Side Projects}

\begin{yearlist}

\item{2023}
     {\href{https://github.com/manuelarto/socialtrustr}{SocialTrustr}}
     {\textbullet~Created a blockchain-based social media framework, to provide traceability and validity of shared content. \newline
     \textbullet~Designed an incentive-based voting system using digital tokens to reduce the spread of fake news. \newline
     \textbf{\textsc{Solidity · Blockchain · Consensus Algorithms}}}
\item{2023}
     {\href{https://github.com/manuelarto/livechat}{Livechat}}
     {\textbullet~Built a full-stack social app with real-time chat and location sharing capabilities among friends, achieving the highest grade (30L) in the 'Mobile Applications' course. \newline
    \textbf{\textsc{Python · Flutter · Websocket · MongoDB · JWT}}}
\item{2022}
     {\href{https://github.com/manuelarto/crazyplayer}{CrazyPlayer}}
     {\textbullet~Implemented an AI player that can play optimally in all possible instances of the M,N,K-game. \newline
     \textbullet~Ranked first in a student tournament with over 50 participants. \newline
    \textbf{\textsc{Java · Game Tree · Algorithms · Data Structure}}}

\end{yearlist}


% ACHIEVEMENTS
\section{Achievements}

\begin{yearlist}

\item[]{2019}
     {Italian Olympiad in Informatics}
     {Competitive programming in C++}

\item[]{May 2019}
     {National IT Competition}
     {Classified 5th in the entire country \newline
     UML design and Java development}

\item[]{Oct 2018}
     {Erasmus+, Vilnius Lithuania}
     {Working full-time in a startup}

\end{yearlist}


% \section{Courses}

% \begin{yearlist}

% \item[Udemy]{May 2020}
%      {Flutter\&Dart - Complete Guide}
%      {42h, \href{https://www.udemy.com/certificate/UC-c6f5a32f-babc-42f9-8a0a-6effadf9e7cd/}{certificate link}}

% \item[Youtube]{2020-2023}
%     {Blockchain Developer, Smart Contract, \& Solidity Course}
%     {Full course beginner to expert, \href{https://github.com/Cyfrin/foundry-full-course-f23}{github repo}}

% \end{yearlist}

\end{document}
